### 2021-06-21 Strings2020/strings5/strings5.tex
Add various updates to homework

	However, in string theory, the Legendre transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
	\begin{equation}
		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) (P - 0)}
		\propto \delta(P - 0)
	\end{equation}
	As $\tau_1$ gets integrated out, we are effectively computing $\Tr' e^{-\beta H}$ where the trace only goes over the $P = 0$ sector of the Hilbert space\footnote{
		This is nicely explained in David Tong's \href{https://www.damtp.cam.ac.uk/user/tong/string.html}{\textit{String Theory}}. See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
	}.

@@

	\begin{enumerate}
	\item The first contributions to the orbifold partition function comes from the states that are invariant reflection $r$; we have:
	\begin{equation}
		\Tr_{S^1/\mbb{Z}_2}
		= \Tr_{S^1} \frac{1 + r}{2}
		= \frac{1}{2}\,{\Tr_{S^1}}
			+ \frac{1}{2}\,{\Tr_{S^1}} \circ r
	\end{equation}
	Acting on $
		q^{L_0 - \tfrac{c}{24}}\,
		\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
	$, the first term gives $\frac{1}{2}\,Z_{S^1}(\tau)$ where $Z_{S^1}$ is the $S^1$ partition function we've obtained in \boxed{1}\,.

>>>>

	However, in string theory, the Legendre transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
	\begin{equation}
		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) (P - 0)}
		\propto \delta(P - 0)
	\end{equation}
	As $\tau_1$ gets integrated out, we are effectively computing $\Tr' e^{-\beta H}$ where the trace only goes over the $P = 0$ sector of the Hilbert space\footnote{
		This is nicely explained in David Tong's \href{https://www.damtp.cam.ac.uk/user/tong/string.html}{\textit{String Theory}}. See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}. See also section 2.1, 2.2 of \arxiv{1912.07654} where the switch between ensembles is reviewed in the context of holography. 
	}.

@@

	\begin{enumerate}
	\item The first contributions to the orbifold partition function comes from the states that are invariant under reflection $r$; we have:
	\begin{equation}
		\Tr_{S^1/\mbb{Z}_2}
		= \Tr_{S^1} \frac{1 + r}{2}
		= \frac{1}{2}\,{\Tr_{S^1}}
			+ \frac{1}{2}\,{\Tr_{S^1}} \circ r
	\end{equation}
	Acting on $
		q^{L_0 - \tfrac{c}{24}}\,
		\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
	$, the first term gives $\frac{1}{2}\,Z_{S^1}(\tau)$ where $Z_{S^1}$ is the $S^1$ partition function we've obtained in \boxed{1}\,.
